Barneby Lives usage example

### 2023-05-15 scripts/project_template.Rmd
added text

```{r}
dummy_pts <- data.frame(
  collectionNo = paste0(rep('RCB', 1000), seq(1:1000)),
  day = c(sample(1:31, size = 1000, replace = T)),
  month = c(sample(5:10, size = 1000, replace = T)),
  year = 2023,
  x = runif(1000, min = -120, max = -100), 
  y = runif(1000, min = 35, max = 48)
) %>% sf::st_as_sf(coords = c(x = 'x', y = 'y'), crs = 4326)

@@

>>>>

```{r dummy data}
dummy_pts <- data.frame(
  collectionNo = paste0(rep('RCB', 1000), seq(1:1000)),
  day = c(sample(1:31, size = 1000, replace = T)),
  month = c(sample(5:10, size = 1000, replace = T)),
  year = 2023,
  x = runif(1000, min = -120, max = -100), 
  y = runif(1000, min = 35, max = 48)
) %>% sf::st_as_sf(coords = c(x = 'x', y = 'y'), crs = 4326)

@@

# first convert from american date format (m%d%year%) to ISO 8601 for both collection and determination date

# second from ISO 8601 prepare notation dates for day of collection and date of determination in text format

```{r Date parsing}

#' create herbarium format dates for specimens
#' 
#' this function will return up to two additional columns with x. 'coll_date_text' a text format for the date of collection and 'det_date_text" a shorter text format date for identification
#' @param x an (sf/tibble/) data frame with both the collection date
#' and determination date
#' @param coll_date date of collection, expected to be of the format 'DD/MM/YYYY', minor checks for compliance to the format will be carried out before returning an error.
#' @param det_date date of determination, same format and processes as above. 
date_parser <- function(x, coll_date, det_date){

    if(missing(det_date)) {

    } else {

    }

}

# FIRST CHECK IF FORMAT IS CORRECT ... 
IsDate <- function(mydate, date.format = "%m/%d/%y") {
  tryCatch(!is.na(as.Date(mydate, date.format)),  
           error = function(err) {FALSE})  
}

date <- c('12/11/2003','07/09/2023', '13/01/2016')
IsDate(date)

stringr::str_split(date, pattern = '/', simplify = T)[,2] # capture the month

date_text <- function(x, col2text){

  text_col <- !!enquo(col2text)

  month_tab <- data.frame(Month_Num = sprintf("%02d", 1:12), Month_Abb = month.abb)
  y <- format(as.Date(x[,col2text], format="%d/%m/%Y"), "%Y")
  d <- format(as.Date(x[,col2text], format="%d/%m/%Y"), "%d")
  m <- format(as.Date(x[,col2text], format="%d/%m/%Y"), "%m")
  m_text <- month_tab[m == month_tab$Month_Num, 'Month_Abb']

 # text <- paste0(d, ' ', m, ', ', y)
  return(m)

}

fourtet <- data.frame(date, tet = c('abc', 'def', 'ggg'))

t <- date_text(fourtet, 'date')

t %>% 
  mutate(dtest = date_text(., ))

t == month_tab$Month_Num
```
